### 2023-02-16 notebooks/conformal.qmd
basic set size loss penalty now for working counterfactual search

```{julia}
M = CCE.ConformalModel(conf_model, mach.fitresult)
generator = CCE.ConformalGenerator()
```

@@

```{julia}
ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
```

>>>>

```{julia}
M = CCE.ConformalModel(conf_model, mach.fitresult)
```

@@

```{julia}
#| output: true
#| echo: false
# Generators:
generators = Dict(
    "Generic (γ=0.5)" => GenericGenerator(opt = opt, decision_threshold=0.5),
    "Generic (γ=0.9)" => GenericGenerator(opt = opt, decision_threshold=0.9),
    "Conformal (λ₂=1)" => CCE.ConformalGenerator(opt=opt, λ=[0.1,1]),
    "Conformal (λ₂=10)" => CCE.ConformalGenerator(opt=opt, λ=[0.1,10]),
)

counterfactuals = Dict([name => generate_counterfactual(x, target, counterfactual_data, M, gen;) for (name, gen) in generators])
# Plots:
plts = []
for (name,ce) ∈ counterfactuals
    plt = plot(ce; title=name, colorbar=false, ticks = false, legend=false, zoom=0)
    plts = vcat(plts..., plt)
end
_n = length(generators)
plot(plts..., size=(_n * 185,200), layout=(1,_n))
```
